Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-24 paper.tex
Add Christian perspective to Response sections

\subsubsection{Response}
An argument based on malware distribution presents a strong case against piracy. Moreover,
we have to acknowledge that the problem targets those with less resources (whether that be
information, financial resources, or technical resources) to protect themselves from the
threats that malware poses. Piracy circumvents mainline distribution channels that may
incorporate secure policies of data integrity, authenticity, and privacy. However, there
are piracy tools and sites that provide some ways to vet the authenticity of a user based
on the user's previous history and relationship with the piracy community. For example,
ThePirateBay, one of the most popular pirating sites, displays the status or class of
their users and holds these users to higher standards in order to retain trust with the
site's end users.~\cite{suprbay:status} Nevertheless, not all sites provide these metrics
or warnings for the average end-user. Instead, the burden is often on the end-user, and
it is not unfair to assume that the average person would not be able to analyze downloaded
software for malware. Thus, to safely make use of piracy tools, one must be aware of the
risks and the ways that they can mitigate those. This is not to say that users need to
reverse engineer all the software they download to look for malicious behavior, but they
do need to be aware of software sources that give them a much better shot at getting an
untainted copy. As mentioned previously, user trust is a crucial component of piracy;
those who choose to enter this domain should be careful to download only from those with a
high reputation in the community---backed by a long time of faithful service.

@@

On the other hand, it is not completely out of the question to imagine a
pirate coming back to some creator (whether that is an individual or a
business) to pay for the content when they are finally able to. As this paper
showed earlier, many pirates are those who do not have the means to pay for
some of the content that they pirate, but perhaps they would if/when they
could.

>>>>

\subsubsection{Response}
An argument based on malware distribution presents a strong case against piracy.
Moreover, we have to acknowledge that the problem targets those with less
resources (whether that be information, financial resources, or technical
resources) to protect themselves from the threats that malware poses. Piracy
circumvents mainline distribution channels that may incorporate secure policies
of data integrity, authenticity, and privacy. However, there are piracy tools
and sites that provide some ways to vet the authenticity of a user based on the
user's previous history and relationship with the piracy community. For example,
ThePirateBay, one of the most popular pirating sites, displays the status or
class of their users and holds these users to higher standards in order to
retain trust with the site's end users.~\cite{suprbay:status}

Nevertheless, not all sites provide these metrics or warnings for the average
end-user. Instead, the burden is often on the end-user, and it is not unfair to
assume that the average person would not be able to analyze downloaded software
for malware. Thus, to safely make use of piracy tools, one must be aware of the
risks and the ways that they can mitigate those. This is not to say that users
need to reverse engineer all the software they download to look for malicious
behavior, but they do need to be aware of software sources that give them a
much better shot at getting an untainted copy. As mentioned previously, user
trust is a crucial component of piracy; those who choose to enter this domain
should be careful to download only from those with a high reputation in the
community---backed by a long time of faithful service.

The issue of trust is one that should not be unfamiliar to Christians. As
Christians, we have a Lord that we can trust in with all our hearts (Prov. 3:5).
As the Psalmist writes, \enquote{It is better to take refuge in the Lord than
to trust in man} (Ps. 118:8). Christians should be slow to put their entire
trust in metrics like those provided by ThePirateBay; while they provide some
founts of trust, they should not immediately encourage Christians to trust
piracy.

@@

On the other hand, it is not completely out of the question to imagine a
pirate coming back to some creator (whether that is an individual or a
business) to pay for the content when they are finally able to. As this paper
showed earlier, many pirates are those who do not have the means to pay for
some of the content that they pirate, but perhaps they would if/when they
could. This possibility of turnaround should be the focus of further research
in the culture of piracy, as the economic argument (for either side) largely
depends on whether pirates would pay for content if they could.

While economic growth can and does benefit the general population, a Christian
response to piracy should take into consideration some of the more complex
aspects of the global marketplace. It is true that the growth of a business can
benefit the employees generally, but the well-being of the consumer should also
be factored into the equation. In the case of commodity software such as
movies, music, or games, the problem that leads to widespread piracy in some
regions is an economic problem; the prices for software or media is set for and
targeted towards an affluent audience. If the companies do not set regional
prices that make their offerings reasonably available to a population, then it
should not come as a surprise that piracy will be widespread. As Christians and
computer scientists, we should be generous to the poor and set regional prices
that make sense for consumers if piracy is negatively affecting the people
(e.g., employees) that we are responsible for (Prov. 14:31; 19:17; Lk. 12:33-34).
